\section{Conclusion}

In this paper, we have presented a novel approach to molecular generation using Conditional Variational Autoencoders (CVAEs) trained on the ChemHarmony dataset. Our method, which combines the power of CVAEs with the robust SELFIES representation, has demonstrated significant potential in the field of drug discovery and molecular design.

The key findings of our study include:

\begin{itemize}
    \item Successful development of a CVAE model capable of generating diverse and chemically valid molecular structures.
    \item Effective utilization of the ChemHarmony dataset, providing a rich foundation for molecular generation with targeted properties.
    \item Demonstration of the model's ability to generate molecules with specific bioactivity profiles, as defined by the assay data in ChemHarmony.
    \item High chemical validity and structural diversity of the generated molecules, showcasing the robustness of our approach.
\end{itemize}

Our work contributes to the growing body of research in AI-driven drug discovery, offering a promising tool for rapid exploration of chemical space and identification of potential drug candidates. The integration of the comprehensive ChemHarmony dataset with advanced machine learning techniques opens new avenues for targeted molecular design.

While our results are encouraging, there are several directions for future research:

\begin{itemize}
    \item Further optimization of the CVAE architecture to improve generation accuracy and property prediction.
    \item Exploration of additional molecular representations and their impact on model performance.
    \item Integration of more complex property prediction tasks, beyond binary bioactivity classification.
    \item Experimental validation of the generated molecules to assess their real-world applicability in drug discovery pipelines.
\end{itemize}

In conclusion, our CVAE-based approach, leveraging the ChemHarmony dataset and SELFIES representation, presents a powerful tool for de novo drug design. As we continue to refine and expand this methodology, we anticipate its increasing role in accelerating the drug discovery process and contributing to the development of novel therapeutic agents.
